---
title: "dicewaRe"
author: "Ken Kleinman"
date: "`March 30, 2015`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

Diceware is a system for generating passphrases from a word list and five six-sided dice.  Simply, one throws five dice, records the throw, and looks up the associated word.  Details about why this is a good idea, security-wise, can be found at http://world.std.com/~reinhold/diceware.html.  There are two main advantages to the system: first, it's relatively simple, or at least possible, to memorize the passphrase, and second, if memorization is difficult, one can record just the dice throws, which may be less likely to attract attention.  The word list can be kept separately or looked up on-line.

This package just collects truly random numbers from random.org and uses them to generate passphrases of the desired length in words.  For example:

```{r}
library(dicewaRe)
phrase(4)
```

If you have the numbers, but lack a hard copy of the canonical list, you can use the **wordlu()** function to find a phrase, one word at a time:

```{r}
wordlu(12543)
```





